Molecular dynamics simulation of synchronization in driven particles

### 2021-02-10 manuscript/manuscript_ajp_2020.tex
started on phases - rabbit hole - do next move to beginning of exercises and then include as subpanel on other figures

  Synchronization 
  %is often studied with simple computational models and
can be visualized 
with phase
plots or Lissajous figures, 
first reported in 1857 \cite{Lissajous1857}.
%and easily generated with a computer code 
%or oscilloscope \cite{Tong1997}. 
A mode-locked system is confined to 
a closed loop in  
parametric phase space % showing the relationship between two periodic functions
with patterns determined by the mode. % frequency ratio,
({\it As we will demonstrate in phase plots in Figs. X, Y, Z}).
%with a frequency generator,
%where two combined frequencies at perpendicular orientations
Note the term phase
has two scientific meanings:  
%``oscillation phase'' and ``phase space.''
%refer to different uses of the word ``phase.''
oscillation phase $\phi_0$ is the constant of the argument
in a periodic function
$\sin{(\omega t + \phi_0)}$ and phase space is
used to characterize oscillating systems with
parametric plots of $v_y$ vs. $y$.

>>>>

  Synchronization 
  %is often studied with simple computational models and
  can be visualized 
  with phase
  plots or Lissajous figures, 
  first reported in 1857 \cite{Lissajous1857}.
  %and easily generated with a computer code 
  %or oscilloscope \cite{Tong1997}. 
  A mode-locked system is confined to 
  a closed loop in  
  parametric phase space % showing the relationship
  %between two periodic functions
  with patterns determined by the mode. % frequency ratio,
  %with a frequency generator,
  %where two combined frequencies at perpendicular orientations
  Note the term phase
  has two scientific meanings:  
  %``oscillation phase'' and ``phase space.''
  %refer to different uses of the word ``phase.''
  oscillation phase $\phi_0$ is the constant of the argument
  in a periodic function
  $\sin{(\omega t + \phi_0)}$ and phase space is
  used to characterize oscillating systems with
  parametric plots of $v_y$ vs. $y$.

  In driven systems,
  the y-position is monotonically increasing.
  We are most interested in the position of the particle
  within the substrate period

  \begin{equation}
  (y mod \lambda) / \lambda
  \end{equation}

  %Juniper so-called ‘phase portraits’, in which the phase velocity, d\phi(t)/dt,is plotted against the phase, \phi(t) = 2\pi (x(t)-\bar{v}t)/\lambda (ref. 53). The
  %REF 53

  \begin{center}
    \begin{figure}[h!]
      \centering
      \includegraphics[width=\columnwidth]{phase.pdf}
      \caption{
        Phase plot of a particle with the same values of $F^{dc}$ and frequency as Fig.~\ref{fig:0}.
      }
      \label{fig:phase}
    \end{figure}
  \end{center}
